Data Cleaning

### 2025-12-04 Data Cleaning.Rmd
Completed code for adding Lag variables to dataset.

```{r}
data <- read.csv("RWAR_dosing_cleaned.csv")
data |>
  mutate(Temp_lag1 = lag(mean_Temp, 1), 
         Temp_lag2 = lag(mean_Temp, 2),
         pH_lag1 = lag(mean_pH, 1),
         pH_lag2 = lag(mean_pH, 2),
         Conductivity_lag1 = lag(conductivity, 1),
         Conductivity_lag2 = lag(conductivity, 2))

>>>>

```{r}
data <- read.csv("RWAR_dosing_cleaned.csv")
lagged_data <- data |>
  mutate(Temp_lag1 = lag(mean_Temp, 1), 
         Temp_lag2 = lag(mean_Temp, 2),
         pH_lag1 = lag(mean_pH, 1),
         pH_lag2 = lag(mean_pH, 2),
         Cond_lag1 = lag(mean_Conductivity, 1),
         Cond_lag2 = lag(mean_Conductivity, 2),
         Turb_lag1 = lag(mean_Turbidity, 1),
         Turb_lag2 = lag(mean_Turbidity, 2))
# Temp
lagged_data$Temp_lag1[1] <- lagged_data$Temp_lag1[2]
lagged_data$Temp_lag2[1:2] <- lagged_data$Temp_lag2[3]
# pH
lagged_data$pH_lag1[1] <- lagged_data$pH_lag1[2]
lagged_data$pH_lag2[1:2] <- lagged_data$pH_lag2[3]
# Conductivity
lagged_data$Cond_lag1[1] <- lagged_data$Cond_lag1[2]
lagged_data$Cond_lag2[1:2] <- lagged_data$Cond_lag2[3]
# Turbidity
lagged_data$Turb_lag1[1] <- lagged_data$Turb_lag1[2]
lagged_data$Turb_lag2[1:2] <- lagged_data$Turb_lag2[3]

lagged_data
lm(Ferric.chloride..mg.L ~ ., data=lagged_data |> select(-c(Timestamp)))
